MSF_Groupwork-NBA_shotlog

### 2016-10-16 MSFGroupwork-NBAHotHand.Rmd
final changes

```{r, echo=FALSE}
#Comparing barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
g1 <- ggplot(data = simulshooter_df, aes(x = streaks )) + geom_bar(fill = 'blue') + labs(title = 'sample shooter')
g2 <- ggplot(data = realshooter_df, aes(x = streaks)) + geom_bar(fill = 'red') + labs(title = 'Kyrie Irving')
```

@@

```{r, echo=FALSE}
graph01 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))+ graph01 + labs(title = "Differences in FGA for games lost/won for particular players") + xlab("Player name") + ylab("FGA")
graph02 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W)) + labs(title = "Differences in FG% for games lost/won for particular players") + xlab("Player name") + ylab("FG%")
graph01
graph02
```

@@

  Ahart (1973). In Kendall, P. and Hollon, S. (1979). Cognitive-behavioral interventions. New York: Academic Press.  
  Economist: As sweet as ever (2015) Available at: http://www.economist.com/blogs/gametheory/2015/06/home-advantage-basketball (Accessed: 16 October 2016).  
  Erculj, F. and Supej, M. (2009). Impact of Fatigue on the Position of the Release Arm and Shoulder Girdle over a Longer Shooting Distance for an Elite Basketball Player. Journal of Strength and Conditioning Research, 23(3), pp.1029-1036.  
  Gilovich, T., Vallone, R. and Tversky, A. (1985) ‘The hot hand in basketball: On the misperception of random sequences’, Cognitive Psychology, 17(3), pp. 295–314. doi: 10.1016/0010-0285(85)90010-6.  
  Mascret, N., Ibáñez-Gijón, J., Bréjard, V., Buekers, M., Casanova, R., Marqueste, T., Montagne, G., Rao, G., Roux, Y. and Cury, F. (2016). The Influence of the ‘Trier Social Stress Test’ on Free Throw Performance in Basketball: An Interdisciplinary Study. PLOS ONE, 11(6), p.e0157215.

>>>>

```{r, echo=FALSE}
#Comparing barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
g1 <- ggplot(data = simulshooter_df, aes(x = streaks )) + geom_bar(fill = 'blue') + labs(title = 'sample shooter')
g2 <- ggplot(data = realshooter_df, aes(x = streaks)) + geom_bar(fill = 'red') + labs(title = 'Kyrie Irving')
grid.arrange(g1, g2, ncol = 2)
```

@@

```{r, echo=FALSE}
graph01 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FGA, colour = W)) + labs(title = "Differences in FGA for games lost/won for particular players") + xlab("Player name") + ylab("FGA")
graph02 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W)) + labs(title = "Differences in FG% for games lost/won for particular players") + xlab("Player name") + ylab("FG%")
graph01
graph02
```

@@

  Ahart (1973). In Kendall, P. and Hollon, S. (1979). Cognitive-behavioral interventions. New York: Academic Press.

  Economist: As sweet as ever (2015) Available at: http://www.economist.com/blogs/gametheory/2015/06/home-advantage-basketball (Accessed: 16 October 2016).

  Erculj, F. and Supej, M. (2009). Impact of Fatigue on the Position of the Release Arm and Shoulder Girdle over a Longer Shooting Distance for an Elite Basketball Player. Journal of Strength and Conditioning Research, 23(3), pp.1029-1036.

  Gilovich, T., Vallone, R. and Tversky, A. (1985) ‘The hot hand in basketball: On the misperception of random sequences’, Cognitive Psychology, 17(3), pp. 295–314. doi: 10.1016/0010-0285(85)90010-6.

  Mascret, N., Ibáñez-Gijón, J., Bréjard, V., Buekers, M., Casanova, R., Marqueste, T., Montagne, G., Rao, G., Roux, Y. and Cury, F. (2016). The Influence of the ‘Trier Social Stress Test’ on Free Throw Performance in Basketball: An Interdisciplinary Study. PLOS ONE, 11(6), p.e0157215.
